---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# educate

Miscellaneous R functions for educational statistics

This package is meant to provide helpful functions for data analysis in educational statistics.

## Installation

```{r eval = FALSE}
devtools::install_github("zief0002/educate")
```

## Watercolor Smoother {#wc-smoother}

The `watercolor_smoother()`, `watercolor_smoother_felix()` and `stat_watercolor_smooth()` functions generate smoothers from bootstrapped samples. The first two functions are stand-alone functions that create ggplot objects (no ggplot syntax required). The third function can be used as a layer directly in ggplot. 

### stat_watercolor_smooth()

```{r wc-smoother-example, message = FALSE, warning = FALSE, fig.asp = 0.5}
# Load libraries
library(ggplot2)
library(scales)
library(educate)

ggplot(data = education, aes(x = salary, y = sat)) +
  stat_watercolor_smooth(method = "lm") +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  theme_classic() +
  scale_x_continuous(name = "Average teacher salary", labels = dollar) +
  ylab("Average SAT score")
```

The figure shows average SAT score plotted as a function of average teacher salaries. The OLS regression line (black) and regression lines for 700 bootstrapped samples (blue) are also displayed. If no method is specified, or `method="loess` is used, the functions will fit a loess smoother. That is demonstrated below along with showing how to change the `k=` and `alpha=` arguments. (Note if the sample size is large and no method is specified a GAM model will be fitted.)

```{r wc-smoother-example-2, message = FALSE, warning = FALSE, fig.asp = 0.5}
ggplot(data = education, aes(x = salary, y = sat)) +
  stat_watercolor_smooth(k = 1000, alpha = 0.03) +
  geom_smooth(se = FALSE, color = "black") +
  theme_classic() +
  scale_x_continuous(name = "Average teacher salary", labels = dollar) +
  ylab("Average SAT score")
```

### watercolor_smoother

Essentially the same plot can be obtained using the `watercolor_smoother()` function which is not embedded as a ggplot layer. The difference is the default number of bootstrap samples is `k=1,000` (rather than `k=700`) and the default alpha level is `alpha=0.03` (rather than `alpha=0.06`).

```{r wc-smoother-example-3, message = FALSE, warning = FALSE, fig.asp = 0.5}
watercolor_smoother(data = education, x = salary, y = sat, method = "lm")
```

### watercolor_smoother_felix()

This function implements code written by [Felix Schonbrodt ](https://www.nicebread.de/visually-weighted-watercolor-plots-new-variants-please-vote/) and also allows for a multicolor palette to be used rather than a moncolor palette. While this is pretty, it may not be any more interpretive than the monocolored palette. (Note: This functionality is not currently implemented in `stat_watercolor_density()` nor `watercolor_smoother()`.)

```{r wc-smoother-example-4, message = FALSE, warning = FALSE, fig.asp = 0.5}
watercolor_smoother_felix(formula = sat~salary, data = education, show.points = TRUE)
```



### 
