---
title: "Graphical Evaluation of Residuals"
author: "Andrew Zieffler"
date: "7/14/2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graphical Evaluation of Residuals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The **educate** package includes the `stat_residual_confidence()` function to generate confidence envelopes for the average residual conditional on a fitted value. This function  can be used as a layer directly in ggplot. Below I illustrate the usage and functionality of each of this function.

### stat_density_confidence()

```{r out.width='60%', fig.align='center'}
# Load libraries
library(broom)
library(ggplot2)
library(educate)

# Fit a linear model
lm.1 = lm(speed ~ dist, data = cars)

# Confidence envelope for average raw residual of 0
augment(lm.1, se_fit = TRUE) |>
  ggplot(aes(x = .fitted, y = .resid)) +
  stat_residual_confidence(model = lm.1, type = "raw") +
  geom_point() +
  geom_smooth(se = FALSE)

# Confidence envelope for average standardized residual of 0
augment(lm.1, se_fit = TRUE) |>
  ggplot(aes(x = .fitted, y = .std.resid)) +
  stat_residual_confidence(model = lm.1, type = "standardized") +
  geom_point() +
  geom_smooth(se = FALSE)
```

You need to provide the fitted model object in the `model=` argument. You also need to provide the residual type (raw or standardized) using the `type=` argument.


Useful optional parameters to the function include:

- `fill=`: Fill color for the confidence envelope. The default is `fill="skyblue"`
- `alpha=`: The level of transparency. The default is `alpha=0.3`



