---
title: "Graphical Evaluation of Residuals"
author: "Andrew Zieffler"
date: "7/14/2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graphical Evaluation of Residuals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The **educate** package includes the `residual_plots()` function to generate plots of the standardized residuals along with confidence envelopes to help evaluate model assumptions. Below I illustrate the usage of this function.

### Evaluate Normality

```{r out.width='60%', fig.align='center'}
# Load libraries
library(broom)
library(ggplot2)
library(educate)

# Fit a linear model
lm.1 = lm(speed ~ dist, data = cars)

# Density plot
residual_plots(lm.1, type = "d")
```

You need to provide the fitted model object (in the `model=` argument; typically unnamed). You also need to provide the plot type using the `type=` argument. Here we use `type="d"` to obtain the density plot of the standardized residuals.


### Evaluate Linearity and Homoskedasticity

```{r out.width='60%', fig.align='center'}
# Load libraries
library(broom)
library(ggplot2)
library(educate)

# Fit a linear model
lm.1 = lm(speed ~ dist, data = cars)

# Density plot
residual_plots(lm.1, type = "s")
```

Here we use `type="s"` to obtain the the scatterplot of the standardized residuals versus the fitted values.


### Both Residual Plots

```{r out.width='80%', fig.align='center', fig.width=8, fig.height=4}
# Load libraries
library(broom)
library(ggplot2)
library(educate)
library(patchwork)

# Fit a linear model
lm.1 = lm(speed ~ dist, data = cars)

# Both residual plots
residual_plots(lm.1, type = "b")

# residual_plots(lm.1)
```

To obtain both plots requires that the `{patchwork}` package is loaded. Here we use `type="b"` to obtain both the density plot of the standardized residuals, and the scatterplot of the standardized residuals versus the fitted values. You can also omit the `type=` argument, since the default is `type="b"`.

