---
title: "Tidy ANOVA Tables"
author: "Andrew Zieffler"
date: "6/30/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tidy ANOVA Tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The `tidy_anova()` function can be used to create an ANOVA table that is outputted as a data frame. This is useful for implementation with `kable()` and other R functions. The function takes as its input an `lm` object.

```{r}
# Fit model with lm()
lm.1 = lm(mpg ~ 1 + wt + hp, data = mtcars)

# Load educate package
library(educate)

# Obtain ANOVA table
tidy_anova(lm.1)
```

## Model-Level Output

The function takes an optional argument of `model=TRUE`. This argument will create the model-level ANOVA table that is commonly presented in APA publications.

```{r}
# Obtain model-level ANOVA table
tidy_anova(lm.1, model = TRUE)
```


## Pretty Tables with kable()

Since `tidy_anova()` outputs a data frame, you can use **knitr**'s `kable()` function to make it look great in a knitted document.

```{r message=FALSE, warning=FALSE}
#Load libraries
library(dplyr)
library(knitr)

# Set knitr options to remove NA values
options(knitr.kable.NA = '')

# Obtain model-level ANOVA table and make it pretty
tidy_anova(lm.1, model = TRUE) %>%
  kable(digits = 2)
```






